---
title: "Assignment 2"
author: "Abigail Burns"
format: html
editor: visual
---

#### Run an exploratory data analysis with R using the TEDS2016 dataset.

```{r}
library(haven)
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
TEDS_2016$PartyID <- factor(TEDS_2016$PartyID, labels=c("KMT","DPP","NP","PFP", "TSU","NPP","NA"))
```

#### What problems do you encounter when working with this dataset?

The dataset has a standard deviation of zero.

```{r}
library(ggplot2)
ggplot(TEDS_2016, aes(PartyID)) + 
  geom_bar(aes(y = (after_stat(count))/sum(after_stat(count)),fill=PartyID)) + 
  scale_y_continuous(labels=scales::percent) +
  ylab("Party Support (%)") + 
  xlab("Taiwan Political Parties") + 
  theme_bw() + 
  scale_fill_manual(values=c("steel blue","forestgreen","khaki1","orange","goldenrod","yellow","grey"))
```

#### How should you deal with missing values?

```{r}
TEDS_2016 <- na.omit(TEDS_2016)
```

#### Explore the relationship between Tondu and other variables female, DPP, age, income, edu, Taiwanese, and Econ_worse. What methods would you use?

```{r}
TEDS_2016$Tondu <- factor(TEDS_2016$Tondu, labels=c("Unification now","Status quo, unif. in future","Status quo, decide later","Status quo forever","Status quo, indep. in future","Independence now","No response"))
table(TEDS_2016$Tondu, TEDS_2016$female)
table(TEDS_2016$Tondu, TEDS_2016$DPP)
table(TEDS_2016$Tondu, TEDS_2016$income)
table(TEDS_2016$Tondu, TEDS_2016$edu)
table(TEDS_2016$Tondu, TEDS_2016$Taiwanese)
table(TEDS_2016$Tondu, TEDS_2016$Econ_worse)
```

```{r}
library(caret)
oneHot <- dummyVars(~., data=TEDS_2016)
TEDS_OneHot <- data.frame(predict(oneHot, TEDS_2016))
model.lm <- lm(Tondu.Independence.now ~ 
                 DPP + age + edu + Taiwanese + Econ_worse + pubwelf5,
               data = TEDS_OneHot)
summary(model.lm)
```

#### Now explore the votetsai variable (vote for DPP candidate Tsai Ing-wen).

It would be redundant to include [both]{.underline} DPP and votetsai in a linear model.

```{r}
table(TEDS_2016$Tondu, TEDS_2016$votetsai)
```

#### Generate a frequency table and bar chart of the Tondu variable with labels.

```{r}
ggplot(TEDS_2016, aes(Tondu)) + 
  geom_bar(aes(y = (after_stat(count))/sum(after_stat(count)),fill=Tondu)) + 
  scale_y_continuous(labels=scales::percent) +
  ylab("Tondu Support (%)") + 
  xlab("Taiwan Tondu Attitudes") + 
  theme_bw() + 
  scale_fill_manual(values=c(
    "red","orange","yellow","goldenrod","steelblue","blue","grey"))
```
